Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-08-01 writeups/dissertation/dissertation.tex
foo

Looking across the plots, including the offset significantly increases model accuracy, for all models, terms, and sites.
Accuracy is improved even when only a single term is used.
Although in this case the weight of the term is irrelevant (only one term, weighting for that term does not matter),
using an offset still improves accuracy since the offset term ensures that only a small number of tags per posts are predicted by the model to be the chosen tags.

@@

The results compare accuracy for models that use a global co-occurrence and user-specific co-occurrence matrix.
For StackOverflow, model accuracy for the user-specific co-occurrence matrix (labeled as ``user sji'') can be compared against the default global co-occurrence matrix.
Accuracy decreases dramatically when a user-specific co-occurrence matrix is used.

@@

Model accuracy when only the single user-customized context predictor is used is relatively poor, and the prior term is a much better predictor.
Further, when this component is combined with the prior component, model performance improves only slightly over performance when only the prior is used.

@@

>>>>

Looking across the plots, including the offset significantly increases model accuracy, for all models, terms, and sites, except that the full Bayesian model without an offset was slightly more accurate on Twitter
(\num{.53} to \num{.60} and \num{.22} to \num{.45} for Bayesian and random permutation for StackOverflow, \num{.31} to \num{.29} and \num{.24} to \num{.25} for Bayesian and random permutation for Twitter).
Accuracy is improved even when only a single term is used.
Although in this case the weight of the term is irrelevant (only one term, weighting for that term does not matter),
using an offset still improves accuracy since the offset term ensures that only a small number of tags per posts are predicted by the model to be the chosen tags.

@@

The results compare accuracy for models that use a global co-occurrence and user-specific co-occurrence matrix.
For StackOverflow, model accuracy for the user-specific co-occurrence matrix (labeled as ``user sji'') can be compared against the default global co-occurrence matrix.
Accuracy decreases dramatically when a user-specific co-occurrence matrix is used for both the Bayesian (\num{.64} to \num{.35}) and random permutation (\num{.58} to \num{.36}) models.

@@

Model accuracy when only the single user-customized context predictor is used is relatively poor (\num{.17} and \num{.21} for Bayesian and random permutation),
and the prior term is a much better predictor (\num{.37}).
Further, when this component is combined with the prior component, model performance improves only slightly over performance when only the prior is used (\num{.37} to \num{.39} for both the Bayesian and random permutation).

@@

Further, if the number of co-occurrences is small, and a user-custom co-occurrence matrix is used, it may be advantageous to use the compressed random permutation model instead of the uncompressed Bayesian model.
For the Twitter popular-users dataset, only a user-custom co-occurrence matrix could be built, and when this matrix is used the compressed random permutation model performed better than the uncompressed Bayesian model.
When the global co-occurrence matrix was removed from the StackOverflow dataset, and a user-custom matrix was used instead, the accuracy for the random permutation model decreased less than the Bayesian model. 
This provides further evidence showing that there is an interaction between dataset size and optimal model:
At lower numbers of co-occurrences the compressed random permutation model is able to perform better than the Bayesian model,
and the Bayesian model surpasses the compressed model at higher co-occurrence counts once the cells in the full co-occurrence matrix stabilize.
